\documentclass{report}
\usepackage{setspace}\onehalfspacing
\usepackage[margin=1in]{geometry}
\usepackage{bm}
\renewcommand{\vec}[1]{\text{\bfseries #1}}


\begin{document}
	\section*{List of Changes}
	
	\begin{itemize}
		\item Fixed margins and position of page numbers to comply with NIP thesis format.
		\item Chap.~1, Sec.~1.2 (Page 3)
		\begin{center}
			...and---due to the computational demands---and focus on... \\
			$\Downarrow$ \\
			...and, due to the computational demands, focus on
		\end{center}
		
		\item Chap.~2 (Page 5)
		\begin{center}
			...the ability reproduce a signal... \\
			$\Downarrow$ \\
			...the ability to reproduce a signal...
		\end{center}
		\item Chap.~2 (Page 5)
		\begin{center}
			...there should be at more than twice... \\
			$\Downarrow$ \\
			...there should be more than twice...
		\end{center}
		\item Chap.~2, Sec.~2.1, Eq.~2.2 (Page 6): ended with a period.
		\item Chap.~2, Sec.~2.2, Eq.~2.3 (Page 7): added description for $f$.
		\item Chap.~2, Sec.~2.3 (Page 8)
		\begin{center}
			The coherence between these two... \\
			$\Downarrow$ \\
			The coherence $\mu$ between these two...
		\end{center}
		\item Chap.~2, Sec.~2.3, Eq.~2.6 (Page 9): ended with a period.
		\item Chap.~2, Sec.~2.4, Eq.~2.11 (Page 10): ended with a period.
		\item Chap.~3, Sec.~3.1 (Page 13)
			\begin{center}
				...value of $\alpha$ was automatically determined... \\
				$\Downarrow$ \\
				...value of $\alpha$ is automatically determined...
			\end{center}
		\item Chap.~3, Sec.~3.1, Fig.~3.1 (Page 12):
			\begin{center}
				Original test signal... \\
				$\Downarrow$ \\
				Original synthesized C$_5$ piano note...
			\end{center}
		\item Chap.~3, Sec.~3.1, Fig.~3.2 (Page 13): leftmost, middle, rightmost $\Rightarrow$ left column, middle column, right column.
		\item Chap.~4, Sec.~4.2.3, Eq.~4.2 (Page 20): equation was not changed. In this notation, $\sigma_{xy}$ refers to the covariance of $x$ \& $y$. The describing sentence that follows it has been revised to clarify this.
		\item Chap.~5 (Page 28)
			\begin{center}
				...audio signals are a tad harder to compressively sample. \\
				$\Downarrow$ \\
				...audio signals are more challenging to compressively sample.
			\end{center}
		\item Chap.~5, Sec.~5.2, Eq.~5.2 (Page 29): ended with a period.
		\item Chap.~5, Fig.~5.2 (Page 33): added a more descriptive caption.
		\item Chap.~5, Fig.~5.4 (Page 34): added a more descriptive caption.
	\end{itemize}
\end{document}